---
title: "Assignment 1-IMDB"
author: "Shude Guo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Preparing data

```{r}
library(keras)
imdb <- dataset_imdb(num_words = 10000)
c(c(train_data, train_labels), c(test_data, test_labels)) %<-% imdb
```

### Data vectorization

```{r}
vectorize_sequences <- function(sequences, dimension = 10000) {
results <- matrix(0, nrow = length(sequences), ncol = dimension)
for (i in 1:length(sequences))
results[i, sequences[[i]]] <- 1
results}
x_train <- vectorize_sequences(train_data)
x_test <- vectorize_sequences(test_data)
y_train <- as.numeric(train_labels)
y_test <- as.numeric(test_labels)
```

### Building network - 2 layers, units = 16, loss function: “binary_crossentropy”, activation = "relu"

```{r}
model <- keras_model_sequential() %>% 
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>% 
  layer_dense(units = 16, activation = "relu") %>% 
  layer_dense(units = 1, activation = "sigmoid")
```

```{r}
model %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy"))
```

### Validation

```{r}
val_indices <- 1:10000
x_val <- x_train[val_indices,]
partial_x_train <- x_train[-val_indices,]
y_val <- y_train[val_indices]
partial_y_train <- y_train[-val_indices]
```

```{r}
model %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results <- model %>% evaluate(x_test, y_test)
results
```

### Using 3 hidden layers
### Building network - 3 layers, units = 16, loss function: “binary_crossentropy”, activation = "relu"

```{r}
model1 <- keras_model_sequential() %>% 
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>% 
  layer_dense(units = 16, activation = "relu") %>% layer_dense(units = 16, activation = "relu") %>% layer_dense(units = 1, activation = "sigmoid")
```

```{r}
model1 %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy"))
```

### Validation

```{r}
val_indices1 <- 1:10000
x_val1 <- x_train[val_indices,]
partial_x_train1 <- x_train[-val_indices,]
y_val1 <- y_train[val_indices]
partial_y_train1 <- y_train[-val_indices]
```

```{r}
model1 %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results1 <- model1 %>% evaluate(x_test, y_test)
results1
```

### Using layers with more hidden units
### Building network - 2 layers, units = 32, loss function: “binary_crossentropy”, activation = "relu"

```{r}
model3 <- keras_model_sequential() %>% 
  layer_dense(units = 32, activation = "relu", input_shape = c(10000)) %>% 
  layer_dense(units = 32, activation = "relu") %>% 
  layer_dense(units = 1, activation = "sigmoid")
```

```{r}
model3 %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy"))
```

### Validation

```{r}
val_indices <- 1:10000
x_val3 <- x_train[val_indices,]
partial_x_train3 <- x_train[-val_indices,]
y_val3 <- y_train[val_indices]
partial_y_train3 <- y_train[-val_indices]
```

```{r}
model3 %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results3 <- model3 %>% evaluate(x_test, y_test)
results3
```

### Building network - 2 layers, units = 16, loss function: “mean_squared_error”, activation = "relu"

```{r}
model5 <- keras_model_sequential() %>% 
  layer_dense(units = 16, activation = "relu", input_shape = c(10000)) %>% 
  layer_dense(units = 16, activation = "relu") %>% 
  layer_dense(units = 1, activation = "sigmoid")
```

```{r}
model5 %>% compile(
  optimizer = "rmsprop",
  loss = "mean_squared_error",
  metrics = c("accuracy"))
```

### Validation

```{r}
val_indices <- 1:10000
x_val5 <- x_train[val_indices,]
partial_x_train5 <- x_train[-val_indices,]
y_val5 <- y_train[val_indices]
partial_y_train5 <- y_train[-val_indices]
```

```{r}
model5 %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results5 <- model5 %>% evaluate(x_test, y_test)
results5
```

### Building network - 2 layers, units = 16, loss function: “binary_crossentropy”, activation = "tanh"

```{r}
model6 <- keras_model_sequential() %>% 
  layer_dense(units = 16, activation = "tanh", input_shape = c(10000)) %>% 
  layer_dense(units = 16, activation = "tanh") %>% 
  layer_dense(units = 1, activation = "sigmoid")
```

```{r}
model6 %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy"))
```

### Validation

```{r}
val_indices <- 1:10000
x_val6 <- x_train[val_indices,]
partial_x_train6 <- x_train[-val_indices,]
y_val6 <- y_train[val_indices]
partial_y_train6 <- y_train[-val_indices]
```

```{r}
model6 %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results6 <- model6 %>% evaluate(x_test, y_test)
results6
```

#### After adjusting different parameters and methods and comparing, the model of 2 layers, units = 16, loss function: "binary_crossentropy", activation = "relu" has the highest accuracy.
#### Units of layer: Accuracy reduced from 16 to 32 units, and accuracy increased from 32 to 64 units.
#### Loss function = “mean_squared_error”: It reduces the loss, but it also reduces the accuracy.
#### Activation = “tanh”: It reduces both loss and accuracy.

### Building network with Regularization - 2 layers, units = 16, loss function: “binary_crossentropy”, activation = "relu"

```{r}
set.seed(123)
model7 <- keras_model_sequential() %>% 
  layer_dense(units = 16, kernel_regularizer = regularizer_l2(0.001), activation = "relu", input_shape = c(10000)) %>% 
  layer_dense(units = 16, kernel_regularizer = regularizer_l2(0.001), activation = "relu") %>% 
  layer_dense(units = 1, activation = "sigmoid")
```

```{r}
model7 %>% compile(
  optimizer = "rmsprop",
  loss = "binary_crossentropy",
  metrics = c("accuracy"))
```

### Validation

```{r}
val_indices <- 1:10000
x_val7 <- x_train[val_indices,]
partial_x_train7 <- x_train[-val_indices,]
y_val7 <- y_train[val_indices]
partial_y_train7 <- y_train[-val_indices]
```

```{r}
model7 %>% fit(x_train, y_train, epochs = 4, batch_size = 512)
results7 <- model7 %>% evaluate(x_test, y_test)
results7
```
